Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis

### 2018-03-27 paper/finalish/article.tex
adds acknowledgement to NZFSSRC
update date + address

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

@@

\address[1]{\orgdiv{Institute of Fundamental Sciences},\orgname{Massey University}, \orgaddress{\state{Palmerston North}, \country{New Zealand}}}

@@

We thank Mid Central Public Health Services, and the Molecular Epidemiology and Public Health Laboratory (mEpiLab, Massey University) for data collection, and the Ministry of Primary Industries for funding the Manawatu campylobacteriosis sentinel surveillance site.

>>>>

\received{27 March 2018}
\revised{27 March 2018}
\accepted{27 March 2018}

@@

\address[1]{\orgdiv{Institute of Fundamental Sciences}, \orgname{Massey University}, \orgaddress{\state{Palmerston North}, \country{New Zealand}}}

@@

We thank Mid Central Public Health Services, and the Molecular Epidemiology and Public Health Laboratory (mEpiLab, Massey University) for data collection, and the Ministry of Primary Industries for funding the Manawatu campylobacteriosis sentinel surveillance site. Nigel French is supported by the New Zealand Food Safety Science and Research Centre.
